\documentclass[12pt]{amsart}

\input{preamble}

\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\Aut}{Aut}
\newcommand{\ot}{\otimes}
\newcommand{\op}{\oplus}
\newcommand{\id}{\mathrm{id}}

\begin{document}

\title{Short notes on General Kummer Theory}
\maketitle

\section{Preliminaries}

\subsection*{Goal:} given a field $K$ and a non-zero natural number $n$, characterize all Galois extensions of $K$ whose Galois group is abelian with exponent $d\mid n$.

\subsection*{Language:} by \textit{abelian} extension we mean a Galois extension $L/K$ with abelian Galois group; by \textit{cyclic} extension we mean a Galois extension $L/K$ with cyclic Galois group.

\subsection*{Reference:} \cite[\S 4.10]{bos18}.

\section{Setting}

\begin{enumerate}
    \item Let $K$ be a field and fix a separable closure $K_{s}$.
    \item Let $n\in \N$ be a non-zero natural number.
    \item Let $G:=\Gal(K_{s}/K)$ be the absolute Galois group.
    \item Let $A$ be an abelian group endowed with the discrete topology and a continuous action of $G$ on $A$ via group automorphisms, which we will denote by $\sigma \cdot a=:\sigma(a)$.
    \item For each intermediate field $K\subseteq L\subseteq K_{s}$ we denote
	\[ A_{L}:=\{ a\in A\mid \sigma(a)=a \text{ for all }\sigma\in \Gal(K_{s}/L)\}. \]
    \item Let $\wp\colon A\to A$ be a $G$-equivariant surjective homomorphism whose kernel, denoted $\mu_{n}$, is a cyclic subgroup of order $n$ of $A_{K}$.
\end{enumerate}

Continuity of the action of $G$ on $A$ ensures that for all $a\in A$ we have
\begin{center}
    \begin{tikzcd}
	G(A/a):=\{ \sigma \in G\mid \sigma(a)=a\}\arrow[open]{r} & G.
    \end{tikzcd}
\end{center}
Hence $G(A/a)$ is also closed in $G$ and corresponds to an intermediate field $K\subseteq K_{s}^{G(A/a)}\subseteq K_{s}$ \cite[4.2/3]{bos18}, let's denote it $K(a)$.

\begin{lm}\label{lm:intermediate}
    The intermediate field $K(a)$ is a finite extension of $K$.
    \begin{proof}
	Let $\{ L_{i} \}_{i\in I}$ be the direct system of all subfields of $K_{s}$ which are finite field extensions of $K$.
	For each $i\in I$, let us denote by
	\[ f_{i}\colon G\to \Gal(L_{i}/K) \]
	the restriction morphism.
	The topology in $G$ is the coarsest one making all the $f_{i}$ continuous.
	Since each $\Gal(L_{i}/K)$ is a finite group, endowed with the discrete topology, it follows that the topology on $G$ should be the smallest topology in which all fibres of the morphisms $f_{i}$ are open.
	But the fibres of all the $f_{i}$ already form a basis for some topology on $G$, so the topology on $G$ can be explicitly described in terms of this basis.

	Since $G(A/a)$ is open and $\id_{K_{s}}\in G(A/a)$, there is some $i\in I$ such that
	\[ f_{i}^{-1}(f_{i}(\id_{K_{s}}))=\Gal(K_{s}/L_{i})\subseteq G(A/a). \]
	From Galois correspondence we deduce now that
	\[ K\subseteq K(a)\subseteq L_{i}, \]
	hence $K(a)$ is also finite over $K$.
    \end{proof}
\end{lm}

More generally, given a subset $\Delta\subseteq A$ we may consider the subgroup
\[ G(A/\Delta):=\{\sigma\in G\mid \sigma(a)=a \text{ for all }a\in \Delta\}=\cap_{a\in \Delta}G(A/a), \]
which is then a closed subgroup but not necessarily an open subgroup.
In any case we obtain an intermediate field $K\subseteq K_{s}^{G(A/\Delta)}\subseteq K_{s}$, which we will denote by $K(\Delta)$.

If $L/K$ is Galois, then the action of $G$ on $A$ restricts to an action of $G$ on $A_{L}$.
Indeed, let $\tau\in G$, $\sigma\in \Gal(K_{s}/L)$ and $a\in A_{L}$.
Since $\Gal(K_{s}/L)\trianglelefteq G$, there is some $\sigma'\in \Gal(K_{s}/L)$ such that
\[ \sigma\tau(a)=\tau\sigma'(a)=\tau(a), \]
hence $\tau(a)\in A_{L}$.
And by definition $\Gal(K_{s}/L)$ acts trivially on $A_{L}$, so we get an induced action of $G/\Gal(K_{s}/L)$ on $A_{L}$.
Using again that $L/K$ is Galois, we may identify this quotient group with $\Gal(L/K)$, obtaining an action of $\Gal(L/K)$ on $A_{L}$.
We can then talk about the cohomology group $H^{1}(\Gal(L/K),A_{L})$.
A function $f\colon \Gal(L/K)\to A_{L}$ is called a \textit{crossed homomorphism} if for all $\sigma,\tau\in \Gal(L/K)$ we have
\[ f(\sigma\tau)=f(\sigma)+\sigma (f(\tau)). \]
A function $f\colon \Gal(L/K)\to A_{L}$ is called a \textit{principal crossed homomorphism} if there exists some $a\in A_{L}$ such that for all $\sigma \in \Gal(L/K)$ we have
\[ f(\sigma)=\sigma(a)-a. \]
Principal crossed homomorphisms form a subgroup of the group of crossed homomorphisms, and the quotient group is then our first cohomology group $H^{1}(\Gal(L/K),A_{L})$.

We are ready now to state the main assumption on which we will rely:

\begin{axiom}
    For every cyclic extension $L/K$ whose degree divides $n$ we have
    \[ H^{1}(\Gal(L/K),A_{L})=0. \]
\end{axiom}

\section{The pairing associated to a subgroup}

Let $C\subseteq A_{K}$ be a subgroup and consider $\wp^{-1}(C)\subseteq A$.
By $G$-equivariance of $\wp$ and our assumption that $C\subseteq A_{K}$, any $\sigma\in G$ restricts to a homomorphism $\sigma\colon \wp^{-1}(C)\to \wp^{-1}(C)$.
If $\sigma(a)=0$ for $a\in \wp^{-1}(C)$, then
\[ \wp(\sigma(a))=\sigma(\wp(a))=\wp(a)=0, \]
because $\wp(a)\in C\subseteq A_{K}$.
Therefore $a\in \mu_{n}\subseteq A_{K}$, and this implies in turn that $\sigma(a)=a=0$.
So the restriction of $\sigma$ is an injective homomorphism $\wp^{-1}(C)\to \wp^{-1}(C)$.
For $a\in \wp^{-1}(C)$ we have
\[ \sigma(a)-a\in \mu_{n} \]
again by $G$-equivariance of $\wp$ and our assumption that $C\subseteq A_{K}$.
So if $\sigma(a)\in \wp^{-1}(C)$, then
\[ \wp(\sigma(a))=\wp(a)\in C \]
and $a\in \wp^{-1}(C)$ as well, showing that the restriction of $\sigma$ is also surjective.
Hence $\sigma$ restricts to a bijection $\wp^{-1}(C)\to \wp^{-1}(C)$.
We obtain in this manner a group homomorphism
\[ G\to \Aut(\wp^{-1}(C)). \]
The kernel of this group homomorphism is $G(A/\wp^{-1}(C))$ by definition.
It is therefore a normal subgroup of $G$, which means in turn that $K(\wp^{-1}(C))/K$ is a Galois extension with Galois group $G_{C}\cong G/G(A/\wp^{-1}(C))$.
In particular, we also obtain an induced action of the Galois group $G_{C}$ on $\wp^{-1}(C)$.

We define now a pairing
\begin{align*}
    G_{C}\times C &\longrightarrow \mu_{n} \\
    (\sigma,c) &\longmapsto \sigma(a)-a, \text{ for }a\in \wp^{-1}(c).
\end{align*}
To check that it is well-defined, pick some other $a'\in \wp^{-1}(c)$.
This elemnt will differ from the previous $a$ by some $b\in \mu_{n}$, hence
\[ \sigma(a')-a'=\sigma(a)+\sigma(b)-a-b=\sigma(a)-a. \]
All good then.
Assume from now on that $\wp(A_{K})\subseteq C$.
We factor then the previous pairing into the pairing that we are interested in:
\begin{align*}
    \langle \cdot,\cdot\rangle \colon G_{C}\times C/\wp(A_{K}) &\longrightarrow \mu_{n} \\
    (\sigma,\bar{c}) & \longmapsto \sigma(a)-a, \text{ for }a\in \wp^{-1}(c).
\end{align*}

\begin{prop}\label{prop:injectivity}
    The pairing $\langle \cdot,\cdot\rangle$ is non-degenerate.
    \begin{proof}
	We have to show that the induced morphisms
	\[ \varphi_{1}\colon G_{C}\to \Hom(C/\wp(A_{K}),\mu_{n}) \quad\text{and}\quad \varphi_{2}\colon C/\wp(A_{K})\to \Hom(G_{C},\mu_{n}) \]
	are injective.

	Suppose that $\sigma\in G_{C}$ is such that $\langle \sigma,\bar{c}\rangle=0$ for all $\bar{c}\in C/\wp(A_{K})$.
	In particular, if $\sigma'\in G$ is a preimage of $\sigma$, then $\sigma(a)=a$ for all $a\in \wp^{-1}(C)$.
	This means precisely that $\sigma'\in G(A/\wp^{-1}(C))$, hence $\sigma=1_{G_{C}}$.

	Suppose now that $c\in C$ is such that $\langle \sigma, \bar{c}\rangle=0$ for all $\sigma\in G_{C}$.
	We want to show that $c\in \wp(A_{K})$, so let $a\in \wp^{-1}(c)$.
	For all $\sigma'\in G$ we have $\sigma'(a)=a$, which means that $a\in A_{K}$ and therefore $\bar{c}=0$.
    \end{proof}
\end{prop}

\begin{prop}\label{prop:finiteness}
    $K(\wp^{-1}(C))/K$ is finite if and only if $(C:\wp(A_{K}))$ is finite.
    \begin{proof}
	Suppose first that $[K(\wp^{-1}(C)):K]$ is finite.
	Then its Galois group $G_{C}$ would be finite as well, so $\Hom(G_{C},\mu_{n})$ is finite.
	But $\varphi_{2}$ is injective by \Cref{prop:injectivity}, so $C/\wp(A_{K})$ must be finite as well.

	Conversely, suppose that $C/\wp(A_{K})$ is finite.
	Again, this implies that $\Hom(C/\wp(A_{K}),\mu_{n})$ is finite, so injectivity of $\varphi_{1}$ shows that $[K(\wp^{-1}(C)):K]$ is finite as well.
    \end{proof}
\end{prop}

\begin{lm}\label{lm:finiteduality}
    Let $n\in \N$ be a non-zero natural number and let $H$ be a finite abelian group with exponent $d\mid n$.
    Then there exists an isomorphism $H\cong \Hom(H,\Z/n\Z)$.
    \begin{proof}
	By the structure theorem for finitely generated abelian groups it suffices to show the result for $H=\Z/d\Z$.
	We first reduce the result to the case $d=n$.
	There is a unique cyclic subgroup $H_{d}\subseteq \Z/n\Z$ of order $d$.
	Every homomorphism $\Z/d\Z\to \Z/n\Z$ factors then through $H_{d}$, so the canonical map
	\[ \Hom(\Z/d\Z,H_{d})\hookrightarrow \Hom(\Z/d\Z,\Z/n\Z) \]
	is an isomorphism.
	Since $H_{d}\cong \Z/d\Z$, it suffices to show that there is an isomorphism
	\[ \Z/d\Z\to \Hom(\Z/d\Z,\Z/d\Z), \]
	i.e.~it suffices to show the case $d=n$.

	In this case we consider the surjective homomorphism
	\begin{align*}
	    \Z & \to \Hom(\Z/d\Z,\Z/d\Z) \\
	    1 & \mapsto \id.
	\end{align*}
	Its kernel is $d\Z$, so passing to the quotient yields the desired isomorphism.
    \end{proof}
\end{lm}

\begin{prop}\label{prop:finitecase}
    If $K(\wp^{-1}(C))/K$ or $(C:\wp(A_{K}))$ are finite, then $\varphi_{1}$ and $\varphi_{2}$ from \Cref{prop:injectivity} are isomorphisms and
    \[ [K(\wp^{-1}(C)):K]=(C:\wp(A_{K})). \]
    \begin{proof}
	By \Cref{prop:finiteness}, if either of the two is finite, so is the other one.
	By \Cref{lm:finiteduality} we have isomorphisms
	\[ C/\wp(A_{K})\cong \Hom(C/\wp(A_{K}),\mu_{n})\quad\text{and}\quad G_{C}\cong \Hom(G_{C},\mu_{n}). \]
	We have
	\begin{align*}
	    [K(\wp^{-1}(C)):K] & = |G_{C}| \\
	    & \leqslant |\Hom(C/\wp(A_{K}),\mu_{n})| \\
	    & = |C/\wp(A_{K})| \\
	    & \leqslant |\Hom(G_{C},\mu_{n}) | \\
	    & = |G_{C}| \\
	    & =[K(\wp^{-1}(C)):K].
	\end{align*}
	Therefore $[K(\wp^{-1}(C)):K]=(C:\wp(A_{K}))$ and $\varphi_{1}$ and $\varphi_{2}$ are isomorphisms.
    \end{proof}
\end{prop}

\begin{prop}\label{prop:infinitecase}
    Even if $[K(\wp^{-1}(C)):K]$ and $(C:\wp(A_{K}))$ are not finite, $\varphi_{1}$ is still an isomorphism and $\varphi_{2}$ induces an isomorphism
    \[ C/\wp(A_{K})\cong \Hom_{\mathrm{cont}}(G_{C},\mu_{n}) \]
    onto the subgroup of continuous homomorphisms.
    \begin{proof}
	Consider the directed system $\{ C_{i} \}_{i\in I}$ of all subgroups $C_{i}$ of $C$ containing $\wp(A_{K})$ and such that $(C_{i}:\wp(A_{K}))$ is finite.
	Since any finite intermediate extension $K\subseteq L\subseteq K(\wp^{-1}(C))$ is contained in some $K(\wp^{-1}(C_{i}))$, we can write
	\[ G_{C}\cong \varprojlim_{i\in I} G_{C_{i}}. \]
	Consider now for each $i\in I$ the commutative diagram
	\begin{center}
	    \begin{tikzcd}
		G_{C}\arrow[hook]{r}{\varphi_{1}}\arrow{d} & \Hom(C/\wp(A_{K}),\mu_{n})\arrow{d} \\
		G_{C_{i}}\arrow{r}{\cong}[swap]{\varphi_{1,i}} & \Hom(C_{i}/\wp(A_{K}),\mu_{n})
	    \end{tikzcd}
	\end{center}
	in which both horizontal arrows are the restrictions.
	Let $f\in \Hom(C/\wp(A_{K}),\mu_{n})$ and consider for each $i\in I$ its restriction $f|_{C_{i}/\wp(A_{K})}$, which comes from a unique $\sigma_{i}\in G_{C_{i}}$.
	This yields a family of automorphisms $(\sigma_{i})_{i\in I}$.
	We claim that this is a compatible family, giving therefore an element in $G_{C}$ which maps to $f$ and proving surjectivity of $\varphi_{1}$.
	To show this, let $i\leqslant j$ and consider the diagram
	\begin{center}
	    \begin{tikzcd}
		G_{C_{j}}\arrow{d}\arrow{r}{\varphi_{1,j}} & \Hom(C_{j}/\wp(A_{K}),\mu_{n})\arrow{d} \\
		G_{C_{i}}\arrow{r}{\varphi_{1,i}} & \Hom(C_{i}/\wp(A_{K}),\mu_{n})
	    \end{tikzcd}
	\end{center}
	in which both vertical arrows are the restrictions.
	We want to check that it commutes.
	The isomorphism $G/G(A/\wp^{-1}(C_{k}))\to G_{C_{k}}$ is given by restriction of automorphisms for all $k\in I$.
	So every $\tau\in G_{C_{j}}$ can be written as $\sigma|_{K(\wp^{-1}(C_{j}))}$ for some $\sigma\in G$.
	For $c\in C_{i}\subseteq C_{j}$ and $a\in \wp^{-1}(c)$ we have then
	\[ \varphi_{1,i}(\tau|_{K(\wp^{-1}(C_{i}))})(\bar{c})=\sigma(a)-a=\varphi_{1,j}(\tau)|_{C_{i}/\wp(A_{K})}(\bar{c}), \]
	showing commutativity of the diagram and thus finishing the proof of bijectivity of $\varphi_{1}$.

	Before discussing the assertion about $\varphi_{2}$, we claim that every continuous homomorphism $g\colon G_{C}\to \mu_{n}$ comes from some homomorphism $g_{i}\colon G_{C_{i}}\to \mu_{n}$ via the restriction $f_{i}\colon G_{C}\to G_{C_{i}}$.
	Indeed, let $\xi\in \mu_{n}$ be a generator.
	Given such $g$ and given some $k\xi\in \mu_{n}$ in the image of $g$, say $k\xi=g(\sigma)$, the preimage $g^{-1}(k\xi)$ is open in $G_{C}$.
	Since the fibers of the restrictions form a basis for the topology on $G_{C}$, there exists some $i_{k}\in I$ such that $f_{i_{k}}^{-1}f_{i_{k}}(\sigma)\subseteq g^{-1}(g(\sigma))$.
	Let now $i=\max_{k}\{ i_{k} \}$ and define
	\begin{align*}
	    g_{i}\colon G_{C_{i}} & \longrightarrow \mu_{n} \\
	    \sigma|_{K(\wp^{-1}(C_{i}))} & \longmapsto g(\sigma).
	\end{align*}
	If $\sigma|_{K(\wp^{-1}(C_{i}))}=\tau|_{K(\wp^{-1}(C_{i}))}$ and $g(\sigma)=k\xi$, then we have $i_{k}\leqslant i$ and therefore
	\[ \tau\in f_{i}^{-1}f_{i}(\sigma)\subseteq f_{i_{k}}^{-1}f_{i_{k}}(\sigma)\subseteq g^{-1}g(\sigma), \]
	showing that $g_{i}$ is well-defined.
	And by construction $g=g_{i}\circ f_{i}$, proving the claim.

	Moving on to the assertion about $\varphi_{2}$, suppose $g\in \Hom(G_{C},\mu_{n})$ is in the image of $\varphi_{2}$, say $g=\varphi_{2}(\bar{c})$.
	Then it is continuous, because the formula we used to define it involves only the continuous action of $G$ on $A$ and the continuous group operations in $A$.
	But we can also check this directly: by homogeneity it suffices to show that
	\[ g^{-1}(0)=\{ \sigma\in G_{C}\mid \sigma(a)-a=0 \text{ for }a\in \wp^{-1}(c) \} \]
	is closed in $G_{C}$, which is true because its preimage under the quotient map is the closed subgroup $G(A/\wp^{-1}(c))$ of $G$.
	Conversely, suppose $g\in \Hom(G_{C},\mu_{n})$ is a continuous homomorphism.
	Then by our previous claim we may find some $i\in I$ such that $g=g_{i}\circ f_{i}$ for some $g_{i}\colon G_{C_{i}}\to \mu_{n}$, where $f_{i}\colon G_{C}\to G_{C_{i}}$ denotes the restriction.
	This means that in the commutative square
	\begin{center}
	    \begin{tikzcd}
		C_{i}/\wp(A_{K}) \arrow[hook]{d}\arrow{r}{\varphi_{2,i}} & \Hom(G_{C_{i}},\mu_{n})\arrow{d} \\
		C/\wp(A_{K}) \arrow{r}{\varphi_{2}} & \Hom(G_{C},\mu_{n})
	    \end{tikzcd}
	\end{center}
	our $g$ lies in the image of the right vertical arrow.
	By \Cref{prop:finitecase} the top horizontal arrow is an isomorphism.
	Hence $g$ also lies in the image of $\varphi_{2}$.
    \end{proof}
\end{prop}

\section{Main Theorem of Kummer Theory}

Recall from the previous section that $C\subseteq A_{K}$ is a subgroup such that $\wp(A_{K})\subseteq C$ and $\{ C_{i} \}_{i\in I}$ is the directed system of all subgroups $C_{i}$ of $C$ containing $\wp(A_{K})$ such that $(C_{i}:\wp(A_{K}))$ is finite.

\begin{lm}\label{lm:fieldwelldefined}
    Then $K(\wp^{-1}(C))/K$ is an abelian extension with exponent $d$ dividing $n$.
    \begin{proof}
	This follows from injectivity of 
	\[ \Gal(K(\wp^{-1}(C))/K)\to \Hom(C/\wp(A_{K}),\mu_{n}), \]
	which was shown in \Cref{prop:injectivity}.
    \end{proof}
\end{lm}

\begin{lm}\label{lm:groupwelldefined}
    Let $L/K$ be a field extension with $L\subseteq K_{s}$.
    Then $C:=\wp(A_{L})\cap A_{K}$ is a subgroup of $A_{K}$ with the property that $\wp(A_{K})\subseteq C$.
    \begin{proof}
	Since $A_{K}\subseteq A_{L}$, it follows that $\wp(A_{K})\subseteq \wp(A_{L})$.
	It remains to show that $\wp(A_{K})\subseteq A_{K}$.
	Let $a\in A_{K}$ and let $\sigma \in G$.
	Then using $G$-equivariance of $\wp$ and the fact that $a\in A_{K}$ we have
	\[ \sigma(\wp(a))=\wp(\sigma(a))=\wp(a), \]
	hence $\wp(a)\in A_{K}$ as well.
    \end{proof}
\end{lm}

\begin{lm}\label{lm:coefficients}
    Let $L:=K(\wp^{-1}(C))$ and $L_{i}:=K(\wp^{-1}(C_{i}))$ for each $i\in I$.
    Then
    \[ A_{L}=\bigcup_{i\in I}A_{L_{i}}. \]
    \begin{proof}
	We show first the inclusion $\supseteq $.
	Let $a\in A_{L_{i}}$ for some $i\in I$, i.e.~for all $\sigma\in G(A/\wp^{-1}(C_{i}))$ we have $\sigma(a)=a$.
	Let then $\sigma\in G(A/\wp^{-1}(C))$, which is by definition the set of automorphisms $\tau\in G$ such that $\tau(b)=b$ for all $b\in \wp^{-1}(C)$.
	Since $a\in \wp^{-1}(C_{i})\subseteq \wp^{-1}(C)$, we deduce that $\sigma(a)=a$.

	We move on to the inclusion $\subseteq $.
	Let $a\in A_{L}$, i.e.~$\sigma(a)=a$ for all $\sigma\in \Gal(K_{s}/L)=G(A/\wp^{-1}(C))$.
	Consider the open subgroup $G(A/a)\subseteq G$.
	The corresponding field $K(a)\subseteq K_{s}$ is finite over $K$, as we saw in \Cref{lm:intermediate}.
	And since $\Gal(K_{s}/L)\subseteq G(A/a)$, we have $K(a)\subseteq L$.
	Since $K(a)$ is finite over $K$ we may find some index $i\in I$ such that $K(a)\subseteq L_{i}$, hence
	\[ a\in A_{K(a)}\subseteq A_{L_{i}}. \]
    \end{proof}
\end{lm}

\begin{thm}
    Viewing abelian extensions of $K$ as subfields of $K_{s}$, there is an inclusion-preserving bijection:
    \begin{align*}
	\{ C\trianglelefteq A_{K} \text{ s.t. } \wp(A_{K})\subseteq C \} & \leftrightarrow \{ L/K \text{ abelian w/ exponent dividing } n\}.
    \end{align*}
    Given $C\trianglelefteq A_{K}$ as above, the corresponding field extension is
    \[ \Phi(C):=K(\wp^{-1}(C)); \]
    and conversely, given $L/K$ as above, the corresponding subgroup is
    \[ \Psi(L):=\wp(A_{L})\cap A_{K}. \]
    \begin{proof}
	The functions $\Phi$ and $\Psi$ are well-defined by \Cref{lm:fieldwelldefined} and \Cref{lm:groupwelldefined} respectively.

	Let us check first that $\Psi\circ \Phi=\id$.
	Let $C\subseteq A_{K}$ be a subgroup such that $\wp(A_{K})\subseteq C$ and let $L=K(\wp^{-1}(C))$.
	We denote $\wp(A_{L})\cap A_{K}$ by $C'$, so that the goal is showing that $C'=C$.

	We start with the inclusion $C\subseteq C'$.
	The subgroup $A_{L}\subseteq A$ consists of all $a\in A$ which are fixed by the automorphisms in $\Gal(K_{s}/L)=G(A/\wp^{-1}(C))$, which in turn are precisely the automorphisms fixing all the elements in $\wp^{-1}(C)$.
	Hence $\wp^{-1}(C)\subseteq A_{L}$ and therefore $C\subseteq \wp(A_{L})\cap A_{K}=C'$.

	Moving on to the other inclusion $C'\subseteq C$, the first thing we claim is that $G(A/A_{L})=G(A/\wp^{-1}(C))$.
	Indeed, from $\wp^{-1}(C)\subseteq A_{L}$ we immediately deduce $G(A/A_{L})\subseteq G(A/\wp^{-1}(C))$.
	And conversely, if $\sigma\in G$ fixes every element in $\wp^{-1}(C)$, then it is an automorphism in $\Gal(K_{s}/L)$ by definition.
	But every element $b\in A_{L}$ satisfies $\tau(b)=b$ for all $\tau\in \Gal(K_{s}/L)$, hence $\sigma$ fixes every element in $A_{L}$ as well.
	Hence $G(A/A_{L})=G(A/\wp^{-1}(C))$.
	In particular, $K(A_{L})=K(\wp^{-1}(C))=L$.
	But we have seen already that $C\subseteq C'$, so $\wp^{-1}(C)\subseteq \wp^{-1}(C')$ and
	\[ L=K(\wp^{-1}(C))\subseteq K(\wp^{-1}(C'))\subseteq K(A_{L})=L. \]
	This implies that $K(\wp^{-1}(C))=K(\wp^{-1}(C'))$.
	In particular, if we are in the situation of finite index, then we can apply \Cref{prop:finitecase} to conclude that $C=C'$.
	Indeed, both field extensions have the same degrees, so both $C$ and $C'$ have the same index over $\wp(A_{K})$.
	Equality follows then from the already proven inclusion $C\subseteq C'$.
	This finishes the case in which $C$ has finite index over $\wp(A_{K})$.
	The general case follows from this case thanks to \Cref{lm:coefficients}, because
	\[ C'=\wp(A_{L})\cap A_{K}=\bigcup_{i\in I}\wp(A_{L_{i}})\cap A_{K}=\bigcup_{i\in I}C_{i}'=\bigcup_{i\in I}C_{i}=C. \]

	It remains to show that $\Phi\circ \Psi=\id$ as well.
	Let $L/K$ be an abelian extension with exponent $d$ dividing $n$.
	Let $C:=\wp(A_{L})\cap A_{K}$.
    \end{proof}
\end{thm}

\newpage
\bibliographystyle{alpha}
\bibliography{main}
\vfill

\end{document}
